\documentclass[hidelinks,12pt,a4paper,numbers=enddot]{scrartcl}

\usepackage[margin=2cm,bottom=3cm]{geometry}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{lmodern}

\title{THE SHELL: Final report}
\author{Claudio Maggioni \and Joey Bevilacqua}

% listings configuration
\lstset{
	basicstyle=\small\ttfamily,
	frame=shadowbox,
	rulesepcolor=\color{gray},
	columns=fullflexible,
	commentstyle=\color{gray},
	keywordstyle=\bfseries\color{red},
	escapeinside={\%*}{*)},
  aboveskip=2em,
  captionpos=b,
  abovecaptionskip=1em,
  belowcaptionskip=1em
}

\begin{document}

\maketitle
\tableofcontents
\newpage

\section{Team member activity}

\begin{table}[h]
\centering
\begin{tabular}{lllll}
\textbf{Author} & \textbf{Lines} & \textbf{Commits} & \textbf{File stats} & \textbf{Distribution} \\ \hline
bevilj  & 415 &   70 &  155 & 56.6 / 24.1 / 46.5 \\
maggicl & 108 &   37 &   64 & 14.7 / 12.8 / 19.2 \\
britea  &  75 &   35 &   26 & 10.2 / 12.1 / 7.8 \\
terehm  &  37 &   28 &   24 &  5.0 / 9.7 / 7.2 \\
omenem  &  15 &   11 &    6 &  2.0 / 3.8 / 1.8 \\
devitg  &  14 &    7 &   10 &  1.9 / 2.4 / 3.0 \\
annoum  &   8 &   24 &    5 &  1.1 / 8.3 / 1.5 \\
feninf  &   8 &    8 &    3 &  1.1 / 2.8 / 0.9 \\
rasicd  &   8 &   10 &    4 &  1.1 / 3.4 / 1.2 \\
alberj  &   7 &    4 &    5 &  1.0 / 1.4 / 1.5 \\
faracm  &   7 &    8 &    5 &  1.0 / 2.8 / 1.5 \\
hijmam  &   6 &    8 &    4 &  0.8 / 2.8 / 1.2 \\
ponzim  &   6 &   10 &    3 &  0.8 / 3.4 / 0.9 \\
luinia  &   6 &    6 &    6 &  0.8 / 2.1 / 1.8 \\
vottad  &   5 &    5 &    5 &  0.7 / 1.7 / 1.5 \\
brunnn  &   4 &    6 &    4 &  0.5 / 2.1 / 1.2 \\
lunghm  &   2 &    5 &    2 &  0.3 / 1.7 / 0.6 \\
montiag &   1 &    1 &    1 &  0.1 / 0.3 / 0.3 \\
marina  &   1 &    2 &    1 &  0.1 / 0.7 / 0.3 \\
vivanr  &   0 &    5 &    0 &  0.0 / 1.7 / 0.0 \\
\end{tabular}
\end{table}

This table shows team member activity using the tool \texttt{git-fame} (\url{https://github.com/casperdcl/git-fame})
\footnote{yes, the repository was mirrored on Github because SVN does not have good stat tools}
The \emph{Distribution} column shows the global percentages for the previous three columns. \\
\textbf{NOTE}: This stats are not entirely accurate: some team members were not able to upload files with their SVN account, so the pages were uploaded by others.

\subsection{Frontpage team}
The frontpage team was able to deliver all its pages on time and with good content. Both the team members offered their
help for doing extra pages for other teams.

\subsection{Filesystem team}
Some of the pages were coauthored with \texttt{team-cmd-basic} members since there was an initial overlap in the
assignment of topics. In this team there were some difficulties with \textit{Jekyll}, but nonetheless they were able
to deliver content.

\textit{Marwan Announ} volunteered to build a multiple-choice quiz feature, eventually not included in the final product
due to lack of time. The code was uploaded just for grading purposes in a separate directory named \texttt{quiz/}.

\subsection{Basic commands team}
This team performed very well. All team members were active and good content creators. They delivered their pages on time
and they offered their help for doing extra pages.

\subsection{Intermediate commands team}
\textit{Gabriele Giacomelli} was absent for the entire duration of the project. Other than that, the team worked well
although there were some problems in getting familiar with the \emph{Jekyll} syntax. Due to the big quantity of pages to
deliver and lack of team members, some help from other teams was needed.

\subsection{Advanced commands team}
\textit{Petro Lukach} was absent for the entire duration of the project. The team was able to deliver the content required,
although some help from other teams was needed.

\subsection{Scripting team}
Both \textit{Marco Conterno}, the team leader, and \textit{Alexander Todorovic} were absent for the entire duration of 
the project. \textit{Marco Tereh} became the \emph{ad interim} team leader. \textit{Matteo Omenetti} was assigned
to this team too.

\textit{Alexander Todorovic} tried to submit some content regarding selection and iteration in \texttt{bash} scripting,
but this content was emailed to \textit{Marco Conterno}. He did not upload it in the SVN repository, nor sent it to the
leading team in any form. The content, recovered mere hours before the deadline, overlaps with some of the work done by
other ``volunteer'' team members, and therefore is was uploaded on a separate directory named \texttt{todorovic/}

\subsection{CSS team}
The team delivered good content for the entire duration of the project. Other than helping other teams when needed, they
were able to grasp the \textit{Jekyll} syntax and work flow very quickly.

\subsection{Leading, bonus and documentation team}
This meta team was composed by \textit{Claudio Maggioni} and \textit{Joey Bevilacqua}. This team did \textit{bonus-1} and
\textit{bonus-2}, wrote all the documentation and reviewed the code and content. Special thanks go to \textit{Joey
Bevilacqua} for doing much of the code reviewing process and being a good vice team leader \footnote{pro-actively self-imposed, in the most positive meaning of the term}.

\section{Use the final product}

\subsection{Building the website}
The final website works with \textit{Jekyll} as planned. In order to build it locally, use the script \texttt{./build.sh}:
a browser window pointing to \url{http://localhost:4000} should open. If the website does not load immediately, reload
the page.

\subsection{Online version}
A live-updating working copy of the website can be found at \url{https://theshell.ch}.

\end{document}
